systemfit: A Package for Estimating\\ Systems of Simultaneous Equations in \proglang{R}

### 2007-11-30 paper/trunk/systemfit_estimation.tex
slightly improved description of the different estimation methods (mainly streamlined notation of the different Omegas, which was suggested by the second referee); noted this in the response to the referees
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/systemfit@863 591db2bd-e0a0-4d22-8c19-2192dbb7da31

The Ordinary Least Squares (OLS) estimator is based on the assumption
that the disturbance terms are not contemporaneously correlated
$(\sigma_{ij} = 0 \; \forall \; i \neq j)$
and have the same variance in each equation
$( \sigma_i^2 = \sigma_j^2 \, \forall \, i, j$,
where $\sigma_i^2 = \E [ u_{it}^2 ])$.
In this case, $\OHat$ in equation~(\ref{eq:ols-wls-sur})
is equal to $I_{G \cdot T}$ and thus, cancels out.
The OLS estimator is efficient,
as long as the disturbances are not contemporaneously correlated.

If the whole system is treated as one single equation,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\sHat^2 I_{G \cdot T}$,
where $\sHat^2$ is the estimated variance of the disturbances.
This assumes that the disturbances of all equations have the
same variance $(\E [ u_{it}^2 ] = \sigma^2 \, \forall \, i)$.
If the disturbance terms of the individual equations
are allowed to have different variances,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

@@

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j)$.
In this case, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance terms in the $i$th equation.
Theoretically, $\sHat_{ii}$ should be the variance of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

@@

If the disturbances are contemporaneously correlated, a Generalized
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
However, the true covariance matrix of the disturbance terms
is generally unknown.
The textbook solution for this problem is
a Feasible Generalized Least Squares (FGLS) estimation.
As the FGLS estimator is based on
an estimated covariance matrix of the disturbance terms,
it is only asymptotically efficient.
In case of an SUR estimator, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\SHat$ is the estimated covariance matrix of the disturbance terms.

@@

The Two-Stage Least Squares (2SLS) estimator
is based on the same assumptions as the OLS estimator.
Accordingly, $\OHat$ in equation~(\ref{eq:2sls-w2sls-3sls})
is equal to $I_{G \cdot T}$ and thus, cancels out.
Like for the OLS estimator,
the whole system can be treated either as one single equation
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\sHat^2 I_{G \cdot T}$,
or the disturbance terms of the individual equations
are allowed to have different variances
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$.

>>>>

The Ordinary Least Squares (OLS) estimator is based on the assumption
that the disturbance terms are not contemporaneously correlated
$(\sigma_{ij} = 0 \; \forall \; i \neq j)$
and have the same variance in each equation
$( \sigma_i^2 = \sigma_j^2 \, \forall \, i, j)$.
In this case, $\OHat$ in equation~(\ref{eq:ols-wls-sur})
is equal to $I_{G \cdot T}$ and thus, cancels out.
The OLS estimator is efficient,
as long as the disturbances are not contemporaneously correlated.

If the whole system is treated as one single equation,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\sHat^2 I_{G \cdot T}$,
where $\sHat^2$ is an estimator for the variance of all disturbances
$(\sigma^2 = \E [ u_{it}^2 ])$.
If the disturbance terms of the individual equations
are allowed to have different variances,
$\OHat$ in equation~(\ref{eq:cov-ols-wls-sur}) is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance term in the $i$th equation.

@@

The Weighted Least Squares (WLS) estimator allows for different variances
of the disturbance terms in the different equations
$( \sigma_i^2 \neq \sigma_j^2 \, \forall \, i \neq j)$,
but assumes
that the disturbance terms are not contemporaneously correlated.
In this case, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$ is the estimated variance
of the disturbance terms in the $i$th equation.
Theoretically, $\sHat_{ii}$ should be the variance of
the (true) disturbances $( \sigma_{ii} )$.
However, they are not known in most empirical applications.
Therefore, true variances are generally replaced by estimated variances
$( \sHat_{ii} )$
that are calculated from the residuals of a first-step OLS estimation
(see section~\ref{sec:residcov}).

@@

If the disturbances are contemporaneously correlated, a Generalized
Least Squares (GLS) estimation leads to efficient parameter estimates.
In this case, the GLS estimator is generally called °Seemingly Unrelated Regression°
(SUR) estimator \citep{zellner62}.
However, the true covariance matrix of the disturbance terms
is generally unknown.
The textbook solution for this problem is
a Feasible Generalized Least Squares (FGLS) estimation.
As the FGLS estimator is based on
an estimated covariance matrix of the disturbance terms,
it is only asymptotically efficient.
In case of a SUR estimator, $\OHat$ in equations~(\ref{eq:ols-wls-sur})
and~(\ref{eq:cov-ols-wls-sur})
is $\SHat \otimes I_T$,
where $\SHat$ is the estimated covariance matrix of the disturbance terms.

@@

The Two-Stage Least Squares (2SLS) estimator
is based on the same assumptions about the disturbance terms as the OLS estimator.
Accordingly, $\OHat$ in equation~(\ref{eq:2sls-w2sls-3sls})
is equal to $I_{G \cdot T}$ and thus, cancels out.
Like for the OLS estimator,
the whole system can be treated either as one single equation
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\sHat^2 I_{G \cdot T}$,
or the disturbance terms of the individual equations
are allowed to have different variances
with $\OHat$ in equation~(\ref{eq:cov-2sls-w2sls-3sls})
equal to $\SHat \otimes I_T$,
where $\sHat_{ij} = 0 \; \forall \; i \neq j$ and
$\sHat_{ii} = \sHat_i^2$.
